\renewcommand\bibname{References}
\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{\numberline{}References}
\bibitem{Neutze} Neutze, R., Wouts, R., van der Spoel, D., Weckert, D. and Hajdu, J., Nature (London) 406, 752-757 (2000)

\bibitem{LCLS} LCLS fact sheet 2014, portal.slac.stanford.edu

\bibitem{RossmanPBCV} Xinzheng Zhang, Ye Xiang, David D. Dunigan, Thomas Klose, Paul R. Chipman, James L. Van Etten, and Michael G. Rossmann, PNAS vol. 108 no. 36 (2011)

\bibitem{pyppaper} Borgstahl, G.E.,  Williams, D.R.,  Getzoff, E.D., Biochemistry 34: 6278-6287 (1995) 

\bibitem{saldinvirus} D. K. Saldin, H. C. Poon, P. Schwander, M. Uddin, and M. Schmidt, Optics Express 19, 17318-17335 (2011)

\bibitem{saldinazimuth} D. K. Saldin, V. L. Shneerson, D. Starodub and J. C. H. Spence Acta Cryst. (2010). A66, 32–37

\bibitem{lucasDNA} Amand A Lucas and Philippe Lambin, Rep. Prog. Phys. 68 (2005) 1181–1249

\bibitem{jacobianger} Abramowitz, Milton; Stegun, Irene A., eds. (December 1972) [1964]. "Chapter 9". Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical Tables. Applied Mathematics Series 55 (10 ed.). New York, USA: United States Department of Commerce, National Bureau of Standards; Dover Publications. p. 355. ISBN 978-0-486-61272-0. LCCN 64-60036. MR 0167642

\bibitem{jacobianger2}Cuyt, Annie; Petersen, Vigdis; Verdonk, Brigitte; Waadeland, Haakon; Jones, William B. (2008), Handbook of continued fractions for special functions, Springer, ISBN 978-1-4020-6948-2

\bibitem{deltafunction}Dragiša Mitrović, Darko Žubrinić (1998). Fundamentals of Applied Functional Analysis: Distributions, Sobolev Spaces. CRC Press. p. 62. ISBN 0-582-24694-6.

\bibitem{harisonjack}A. Jack and S. C. Harrison, “On the interpretation of small-angle x-ray solution scattering from spherical viruses” J. Mol. Biol. 99, 15–25 (1975).

\bibitem{norahcohan} N. V. Cohan "The spherical harmonics with the symmetry of the icosahedral group", Mathematical Proceedings of the Cambridge Philosophical Society 53, 28-38 (1958).

\bibitem{pdb1m4x} Nandhagopal, N., Simpson, A., Gurnon, J.R., Yan, X., Baker, T.S., Graves, M.V., Van Etten, J.L., Rossmann, M.G. "The Structure and Evolution of the Major Capsid Protein of a Large, Lipid containing, DNA virus" Proc.Natl.Acad.Sci.USA 99: 14758-14763 (2002) 

\bibitem{pdb2phy} Borgstahl, G.E., Williams, D.R., Getzoff, E.D. "1.4 A structure of photoactive yellow protein, a cytosolic photoreceptor: unusual fold, active site, and chromophore."  Biochemistry 34: 6278-6287 (1995)
\bibitem{nanokassemeyer} Stephan Kassemeyer et all, "Femtosecond free-electron laser x-ray diffraction data sets for algorithm development" Optics Express 20: 4149-4158 (2012)

\bibitem{pendry1974} Pendry, J. B., {\it Low Energy Electron Diffraction} (Academic, London, 1974).

\bibitem{oszlanyi2004} Oszl\'{a}nyi G. and S\"{u}to A., Acta Cryst. A {\bf 60}, 134-141 (2004).

\bibitem{oszlanyi2005} Oszl\'{a}nyi G. and S\"{u}to A., Acta Cryst. A {\bf 61}, 147-151 (2005). 

\bibitem{caspar1962} Caspar, D. L. D., and Klug, A. Cold Spring Harbor Symp. Quant. Biol. {\bf 27}, 1-24 (1962).

\bibitem{kam1978} Kam, Z., Macromolecules {\bf 10}, 927 (1978).

\bibitem{saldin2009} Saldin, D.K., Shneerson, V. L., Fung, R., and Ourmazd, A., J. Phys: Condens. Matter {\bf 21}, 134014 (2009).

\bibitem{tinkham}Tinkham M 2003 Group Theory and Quantum Mechanics (Dover: Courier)

\bibitem{pande2014} Pande, K., Schwander, P., Schmidt, M., and  Saldin, D. K, Phil. Trans. Roy. Soc. B,  {\bf 369}, 20130332 (2014).

\bibitem{pande2} K. Pande, M. Schmidt, P. Schwander, and D. K. Saldin, Structural Dynamics, 2, 024103 (2015).

\bibitem{saldin2010} D. K. Saldin, H. C. Poon, V. L. Shneerson, M. Howells, H. N. Chapman, R. Kirian, K. E. Schmidt, and J. C. H. Spence, Phys. Rev. B 81, 174105 (2010).

\bibitem{PJHO} P. J. Ho, D. Starodub, D. K. Saldin, V. L. Shneerson, A. Ourmazd, and R. Santra, J. Chem. Phys. 131, 131101 (2009).

\bibitem{PoonFiber} H.C. Poon, P. Schwander, M. Uddin, and D. K. Saldin, Phys. Rev. Lett. 110, 265505 (2013).

\bibitem{Stuhrmann} D. Svergun and H. B. Stuhrmann, “New developments in direct shape determination from small-angle scattering 1. Theory and model calculations,” Acta Crystallogr., Sect. A: Found. Crystallogr. 47, 736–744 (1991).

\bibitem{HLIU2012} H. Liu, B. K. Poon, A. J. E. M. Janssen, and P. H. Zwart, “Computation of fluctuation scattering profiles via three-dimensional zernike polynomials,” Acta Crystallogr., Sect. A: Found. Crystallogr. 68, 561–567 (2012).
\bibitem{HLIU20013} H. Liu, B. K. Poon, D. K. Saldin, J. C. H. Spence, and P. H. Zwart, “Three-dimensional single-particle imaging using angular correlations from x-ray laser data,” Acta Crystallogr., Sect. A: Found. Crystallogr. 69, 365–373 (2013).
\bibitem{Donatelli} Jeffrey J. Donatelli, Peter H. Zwart, and James A. Sethian, "Iterative phasing for fluctuation X-ray scattering", 10286–10291, doi: 10.1073/pnas.1513738112
\bibitem{2BUK} Jones, T.A., Liljas, L.,Structure of Satellite Tobacco Necrosis Virus After Crystallographic Refinement at 2.5 A Resolution., J.Mol.Biol. 177: 735 (1984)
\bibitem{Kittel} Charles Kittel, Introduction to Solid State Physics, 2004 
\bibitem{saldinNJournal} D K Saldin, V L Shneerson, M R Howells, S Marchesini, H N Chapman, M Bogan, D Shapiro, R A Kirian, U Weierstall, K E Schmidt and J C H Spence, New J. Phys. 12, 035014 􏰈2010􏰉
\bibitem{saldin2010PhysB} D. K. Saldin, H. C. Poon, V. L. Shneerson, M. Howells, H. N. Chapman, R. A. Kirian, K. E. Schmidt, and J. C. H. Spence, Phys. Rev. B 81, 174105 (2010).
\bibitem{CromerMann}D. T. Cromer, J. B. Mann, X-ray scattering factors computed from numerical Hartree-Fock wave functions, Acta Cryst. (1968). A24, 321-324
\bibitem{tablecryst}INTERNATIONAL TABLES FOR X-RAY CRYSTALLOGRAPHY, MacGillavry, Kluwer Academic Pub
\bibitem{pdbformat} Berman, Helen M. "The protein data bank: a historical perspective." Acta Crystallographica Section A 64.1 (2007): 88-95
\bibitem{pdbformat2} Chimera Team, University of California San Diego, "https://www.cgl.ucsf.edu/chimera/docs/UsersGuide/tutorials/pdbintro.html"
\bibitem{cubicsplineBartel} Bartels, R. H.; Beatty, J. C.; and Barsky, B. A. "Hermite and Cubic Spline Interpolation." Ch. 3 in An Introduction to Splines for Use in Computer Graphics and Geometric Modelling. San Francisco, CA: Morgan Kaufmann, pp. 9-17, 1998.
\bibitem{cubicsplineBurden}Burden, R. L.; Faires, J. D.; and Reynolds, A. C. Numerical Analysis, 6th ed. Boston, MA: Brooks/Cole, pp. 120-121, 1997.
\bibitem{babinet} Babinet, A.,  Compt. Rend. Acad. Sci. 4:638 (1837).
\bibitem{cheetah}  https://github.com/antonbarty/cheetah-old/wiki
\bibitem{spenceP} Spence J.C.H. private communication.
\bibitem{Drenth} Drenth, J., Principles of Protein X-Ray Crystallography (Springer Advanced Texts in Chemistry) (Springer: New York, 1994).
\bibitem{Munke} Munke, A., et al., Sci. Data, 3: 160064 doi: 10.1038/sdata 2016.64 (2016).
\bibitem{Casper} Caspar, D. L. D., and Klug, A. Cold Spring Harbor Symp. Quant. Biol. 27: 1-24 (1962).
\bibitem{kimmedicine} Kim, S. S., Wibowo, S., and Saldin, D. K., Internal Medicine Review, in press.
\bibitem{kurta} Kurta, R.P., Dronyak, R., Altarelli, M, Weckert, E., and Vartanyants, I. A., New Journal of Physics 15: 013059
\bibitem{pedrini} Pedrini B., Menzel, A., Guizar-Sicairos, M., Guzenko, V. A.,  Gorelik, S. David, C., Patterson, B. A., Abela, R., Nature Commun. 14:1647 (2013).
\end{thebibliography}

